Effectful Semantics for Substructural SSA

### 2023-11-10 pldi24/paper.tex
Cleaned up figure slightly

\usepackage{listings}
\usepackage{xcolor}
\usepackage{subfig}
\usepackage{fancyvrb}

@@

\newsavebox\notssafib

\begin{lrbox}{\notssafib}
\begin{minipage}{0.3\textwidth}
\begin{lstlisting}[frame=none,numbers=none]
'entry:
  m = 0
  n = 1
  brz i 'exit 'loop
'loop:
  t = add m n
  m = n
  n = t
  N = sub i 1
  brz i 'exit 'loop
'exit:
  ret m
\end{lstlisting}
\end{minipage}
\end{lrbox}

\newsavebox\ssafib

\begin{lrbox}{\ssafib}
\begin{minipage}{0.3\textwidth}
\begin{lstlisting}[frame=none,numbers=none]
'entry:
  m0 = 0
  n0 = 1
  brz N 
    'exit (m0) 
    'loop (i, m0, n0)
'loop(i0, m1, n1):
  m2 = n1
  n2 = add m1 n1
  i1 = sub i0 1
  brz z1 
    'exit (m2) 
    'loop (i1, m2, n2)
'exit(m3):
  ret m3
\end{lstlisting}
\end{minipage}
\end{lrbox}

\newsavebox\ourfib

\begin{lrbox}{\ourfib}
\begin{minipage}{0.3\textwidth}
\begin{lstlisting}[frame=none,numbers=none]
let m0 = 0;
let n1 = 1;
if eq i 0 {
  br 'exit(m0)
} else {
  br 'loop(i, m0, n0)
} where
'loop(i0, m1, n1) =>
  let m2 = n1;
  let n2 = add m1 n1;
  let i1 = sub i0 1;
  if eq i1 0 {
    br 'exit(m2)
  } else {
    br 'loop(i1, m2, n2)
  }
'exit(m3) => ret m3
\end{lstlisting}
\end{minipage}
\end{lrbox}

\begin{figure}
  \centering
  \subfloat[3-address code]{\usebox\notssafib}
  \quad
  \subfloat[Basic blocks with arguments]{\usebox\ssafib}
  \quad
  \subfloat[Our syntax]{\usebox\ourfib}
  \caption{A simple program for computing the \texttt{i}th Fibonacci number, represented as 3-address code, basic-blocks with arguments, and in our SSA syntax}
  \Description{}
  \label{fig:ssa-examples}
\end{figure}

>>>>

\usepackage{listings}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage{fancyvrb}

@@

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.33\textwidth}
    \begin{BVerbatim}[baseline=t, gobble=3]
    'entry:
      m = 0
      n = 1
      brz i 'exit 'loop
    'loop:
      t = add m n
      m = n
      n = t
      N = sub i 1
      brz i 'exit 'loop
    'exit:
      ret m
    \end{BVerbatim}
    \caption{3-address code}
  \end{subfigure}
  \begin{subfigure}[t]{0.32\textwidth}
    \begin{BVerbatim}[baseline=t, gobble=3]
      'entry:
      m0 = 0
      n0 = 1
      brz N 
        'exit (m0) 
        'loop (i, m0, n0)
    'loop(i0, m1, n1):
      m2 = n1
      n2 = add m1 n1
      i1 = sub i0 1
      brz z1 
        'exit (m2) 
        'loop (i1, m2, n2)
    'exit(m3):
      ret m3
    \end{BVerbatim}
    \caption{Basic blocks with arguments}
  \end{subfigure}
  \begin{subfigure}[t]{0.33\textwidth}
    \begin{BVerbatim}[baseline=t, gobble=3]
    let m0 = 0;
    let n1 = 1;
    if eq i 0 {
      br 'exit (m0)
    } else {
      br 'loop (i, m0, n0)
    } where
    'loop(i0, m1, n1) =>
      let m2 = n1;
      let n2 = add m1 n1;
      let i1 = sub i0 1;
      if eq i1 0 {
        br 'exit (m2)
      } else {
        br 'loop (i1, m2, n2)
      }
    'exit(m3) => ret m3
    \end{BVerbatim}
    \caption{Our syntax}
  \end{subfigure}
  \caption{A simple program for computing the \texttt{i}th Fibonacci number, represented as 3-address code, basic-blocks with arguments, and in our SSA syntax}
  \Description{}
  \label{fig:ssa-examples}
\end{figure}
